### 2015-05-13 whoop.tex
update

Currently, \whoop only supports mutexes and spinlocks from the Linux kernel APIs. However, it is relatively easy to enhance our tool with knowledge of other locking primitives. If \whoop cannot infer a lock, e.g. because it was created dynamically or was indexed from an array of locks, it will exit with a warning. The reason behind this is twofold: (i) it is arguably hard to detect such locks using static analysis; and (ii) we want to advocate the use of good locking practices when developing drivers for the Linux kernel.

>>>>

Currently, \whoop only supports mutexes and spinlocks that are available in the Linux kernel APIs. However, it is relatively easy to enhance our tool with knowledge of other locking primitives. If \whoop cannot infer a lock, e.g. because it was created dynamically or was indexed from an array of locks, it will exit with a warning. The are two reasons behind this: (i) it is arguably hard to detect such locks using static analysis; and (ii) we want to advocate the use of good locking practices when developing drivers for the Linux kernel.
